Sequential rank agreement methods for comparison of ranked lists

### 2015-06-10 latex/paper.Rnw
Smaller update

The agreement, $A(X_p)$, cannot be computed directly for all
predictors when we have censored lists because we only do not know the
exact rank assigned to each item in all lists.  Instead we assume that
the rank assigned to an item $X_p$ that is not present in list $l$
(i.e., is censored) is uniformly distributed among the ranks that have
\emph{not} been assigned for list $l$.  The rankings within a single
list are clearly not independent since each rank must appear exactly
in each list. Thus we cannot simply assign

Thus, by randomizing unobserved items as described in
\eqref{formula:censored-agreement}

The algorithm is described in
detail in Algorithm~\ref{sra-algorithm}.

@@

>>>>

The agreement, $A(X_p)$, cannot be computed directly for all
predictors in the presence of censored lists because the exact rank
for some item is unknown in some of the lists.  The rankings within a
single list are clearly not independent since each rank must appear
exactly once in each list. Thus we cannot simply assign the same
number (e.g., the mean of the unassigned ranks) to the censored items
since that would result in less variation of the agreement, and it
would artificially introduce a (downward) bias of agreement for items
that are censored in multiple lists.

Instead we assume that the rank assigned to an item $X_p$ that is not
present in list $l$ (i.e., is censored) is uniformly distributed among
the ranks that have \emph{not} been assigned for list $l$. By
randomizing unobserved items we attain one realization of the rankings
where all lists are fully observed. By randomizing a large number of
times we can compute \eqref{def:sra} for each realization, and then
compute the sequential rank agreement as the pointwise (for each
depth) average of the rank agreements. The algorithm is described in
detail in Algorithm~\ref{sra-algorithm}.

@@

Discuss assumption

Present stuff that is long enough

information

in
\eqref{formula:censored-agreement}
